% !TEX root =  ../report.tex
\section{Conclusion \& Improvements}
A whole lot can be improved about the wire-frame now that the results are in. There were twenty-one issues to look through and see how practical they would be to implement.

\subsection{Usability}
First of all it can be said that a whole lot of issues lay in the area of usability. This will include changing some prompt-text. This is a very good improvement which wouldn't have found if we just reviewed the wire-frames ourselves. These changes will make the user less confused and more familiar with the app. 
these changes include:
\begin{itemize}
    \item Problem 5: Change TaskList into Task List in the creation screen
    \item Problem 8: Change the "choose a ...." to "name of ..."
    \item Problem 9: Change term "Board Id" to "Board key"
    \item Problem 10: Change the text on the change server button to : "Join new Server"
    \item Problem 13: Delete the underline and make the text bold so that it is still obvious that it is a header.
    \item Problem 16: Change the "Select a boardId" to "Enter a board key".
\end{itemize}

\subsection{Buttons}
Then there are the issues with misplaced / unnatural buttons. This is also something we should immediately improve upon. This includes repositioning, re-texturing and the addition of buttons. 
The issues regarding the buttons are and their implied changes are: 
\begin{itemize}
    \item Problem 2: The addition of a "Delete" button for a TaskList.
    \item Problem 3: Re-style the buttons for "Finish" and "Delete" in card view to be inline with the rest of the application.
    \item Problem 6: The addition of a "Delete" button for a Board .
    \item Problem 7: The addition of an "exit" button in "Add Task List".
    \item Problem 14: Re-style edit buttons to be just a pencil, such that it does not imply such importance as it does now. 
\end{itemize}
\newpage
\subsection{Error Messages}
The next section of Problems had to do with error messages. These are really important for a good working application so these should have really high priority. The amount of issues in this category can also be attributed to just making a general error message wire-frame, and not one for every possible error in the system. But if the application is finished, the application does definitely need an error message for every possible situation, so this is more of a list of all the error messages that need to be crafted.
\begin{itemize}
    \item Problem 1: Make the error message customize-able for every possible situation.
    \item Problem 11: Make a error message that appears when the field is empty and the user tries to submit.
    \item Problem 12: Again, make the error message modular so that the wire-frame can be used everywhere but the message can be changed.
    \item Problem 21: Make a error that lets you double check if you want to delete something.
\end{itemize}

\subsection{Missing menus}
This section of problems has to do with missing screens. Screens are necessary for requesting information from the user and creating and editing elements in the program. The issues in this section are characterized by an oversight when creating the mocks. These screens are must-have's in out application. 
\begin{itemize}
    \item Problem 17: Make Customization page, for changing Board and UI colours.
    \item Problem 18: Make a screen to add sub-tasks and tags to cards
    \item Problem 19: Make a screen for tag management
    \item Problem 20: This problem is connected to problem 17 in that it points out that the colors used in the application might be hard to discern for visually impaired people, since the color of buttons was only slightly darker than the background, this could be solved in a color picker or by making the buttons higher contrast. 
\end{itemize}

\subsection{Added Functionality}
There were also problems with the clearness of some functions. This is taken together in this category with functions that were simply missing, though they are advanced requirements so its not the biggest problem. But the problems which deal with the clearness of certain functions do most certainly need to be addressed.
\begin{itemize}
    \item Problem 4: The name of the Task List and BoardName need to be made editable if the user clicks on edit, this is a "in-place" edit. This could also be made a bit clearer by making the button a pencil instead of making it say "edit".
    \item Problem 15: The functionality to add tags to cards needs to be added, and in the same vain, the functionality to change the color of a specific card.
\end{itemize}
\subsection{Final design}
Our final GUI design can be found at appendix \ref{appendix:b}.