% !TEX root =  ../report.tex
\section{Methods}
\subsection{Experts}
For our Heuristic Usability Evaluation, we recruited a group of experts from the Computer Science and Engineering department at our university. The group consisted of five individuals who are currently in their first year of the program. While they may be considered relatively new to the field, they have recently completed a course on Web and Database Technology and have gained foundational knowledge on usability and user-centered design principles. 
Additionally, they are highly motivated to expand their knowledge in this area and have demonstrated a keen interest in improving the user experience of digital products. Although They are not professionals in the field yet, we are confident that the insights and feedback provided by this group of experts will be useful in identifying usability issues and making recommendations for improvement.
\subsection{Procedure}
Our exerts were provided with a PDF document containing all our wire-frames. The experts were also provided a list of the heuristic principles and video's about how to conduct a heuristic usability evaluation. In these videos the experts were told to do the review on an individual basis. In the videos it was explained that the experts should examine the wire-frames over a period of around 2 hours. During which they should look over the entire wire-frames multiple times to try to find all the points of improvement. 
During the heuristic usability evaluation the experts were only able to view the wire-frames we had provided and the list of heuristic usability values. The list that they had to use was:\cite{heuristic}
\begin{enumerate}
\item Visibility of system status
\item Match between system and the real world
\item User control and freedom
\item Consistency and standards
\item Error prevention
\item Recognition rather than recall
\item Flexibility and efficiency of use
\item Aesthetic and minimalist design
\item Help users recognize, diagnose, and recover from errors
\item Help and documentation
\end{enumerate}
The reviewers were asked to evaluate the mock and write down a brief description of the problem, the anticipated difficulties that the user will encounter as a consequence of the problem, the specific context in which the problem could occur and a description of the cause of the problem. 
After this step the experts were asked to discuss in a group to merge all the found problems into one list of problems and to add the specific heuristic usability value that the problem breached. 
\subsection{Measures}
Our experts were asked to structure their review as a list of problems. Once they had all created their individual lists, all lists were merged into one (removing duplicates). This created a final pdf file, which we received from the experts. We asked our experts to deliver their problems in the following format:\cite{problem}
\begin{enumerate}
\item\textbf{Problem Description:} a brief description of the problem
\item\textbf{Likely/actual difficulties:} the anticipated difficulties that the user will encounter as a consequence of the problem
\item\textbf{Specific contexts:} the specific context in which the problem may occur
\item\textbf{Assumed causes:} description of the cause(s) of the problem
\end{enumerate}